Sexual selection and speciation: a macro-evolutionary approach

### 2018-10-07 Sexual Selection and Extinction.Rmd
Manuscript and Supp Headings Changed

###Time-constant

We also ran a time-constant MCC of BAMM
```{r, eval=FALSE}
#Read in the tree and MCMC to check for convergence 
MCC.BAMM.tree  <- read.tree("data/BAMM_MCC/MCC.passerine.tre") #Same as other MCC tree already loaded
MCC.BAMM.Constant.mcmc <- read.csv( "data/BAMM_MCC/TimeConstant/tree_MCC_Constant_mcmc_out.txt" , stringsAsFactors=F)

#Looks like it has converged so let's discard burn in: 
burnstart <- floor(0.1 * nrow(MCC.BAMM.Constant.mcmc))
postburn <- MCC.BAMM.Constant.mcmc[burnstart:nrow(MCC.BAMM.Constant.mcmc), ]

cbind(effectiveSize(postburn$N_shifts), effectiveSize(postburn$logLik)) %>% `colnames<-`(c("N_Shifts", "logLik")) %>% `rownames<-`("Effective Sample Size") %>% pander()

# Read in Event Data
MCC.BAMM.ED.Constant <- getEventData(MCC.BAMM.tree,  "data/BAMM_MCC/TimeConstant/tree_MCC_Constant_event_data.txt", burnin=0.1, nsamples=1000)
saveRDS(MCC.BAMM.ED.Constant, 'data/MCC.BAMM.ED.Constant.rds')
#From the Event Data we can extract

css2 <- credibleShiftSet(MCC.BAMM.ED.Constant, expectedNumberOfShifts=100, threshold=5, set.limit = 0.95)

css2$number.distinct

plotPrior(MCC.BAMM.Constant.mcmc, expectedNumberOfShifts=100)

MCC.BAMM.df.Constant <- BAMM.extraction.function(MCC.BAMM.ED.Constant)

MCC.BAMM.df.Constant %>% ggplot(aes(x = mean.lambda, y = MCC.BAMM.df$mean.lambda))+
  geom_point()
cor(MCC.BAMM.df.Constant$mean.lambda, MCC.BAMM.df$mean.lambda)
```

@@

##Subsetted analysis with Armenta data

@@

##Analysis using male-bias measure of sexual selection

>>>>

<!-- ###Time-constant -->

<!-- We also ran a time-constant MCC of BAMM -->
<!-- ```{r, eval=FALSE} -->
<!-- #Read in the tree and MCMC to check for convergence  -->
<!-- MCC.BAMM.tree  <- read.tree("data/BAMM_MCC/MCC.passerine.tre") #Same as other MCC tree already loaded -->
<!-- MCC.BAMM.Constant.mcmc <- read.csv( "data/BAMM_MCC/TimeConstant/tree_MCC_Constant_mcmc_out.txt" , stringsAsFactors=F) -->

<!-- #Plot of convergence can be generated by: -->
<!-- #plot(MCC.BAMM.mcmc$logLik ~ MCC.BAMM.mcmc$generation) -->

<!-- #Looks like it has converged so let's discard burn in:  -->
<!-- burnstart <- floor(0.1 * nrow(MCC.BAMM.Constant.mcmc)) -->
<!-- postburn <- MCC.BAMM.Constant.mcmc[burnstart:nrow(MCC.BAMM.Constant.mcmc), ] -->

<!-- #We can also check effective population sizes of the log-likelihhod and number of shift events in each sample -->
<!-- #We want at least 200 (although that's on the low side) -->

<!-- cbind(effectiveSize(postburn$N_shifts), effectiveSize(postburn$logLik)) %>% `colnames<-`(c("N_Shifts", "logLik")) %>% `rownames<-`("Effective Sample Size") %>% pander() -->

<!-- # Read in Event Data -->
<!-- MCC.BAMM.ED.Constant <- getEventData(MCC.BAMM.tree,  "data/BAMM_MCC/TimeConstant/tree_MCC_Constant_event_data.txt", burnin=0.1, nsamples=1000) -->
<!-- saveRDS(MCC.BAMM.ED.Constant, 'data/MCC.BAMM.ED.Constant.rds') -->
<!-- #From the Event Data we can extract  -->

<!-- css2 <- credibleShiftSet(MCC.BAMM.ED.Constant, expectedNumberOfShifts=100, threshold=5, set.limit = 0.95) -->

<!-- #Now we obtain the number of distinct shifts: (Out of 1000 samples this is super high, essentially each one is distinct) -->

<!-- css2$number.distinct -->

<!-- plotPrior(MCC.BAMM.Constant.mcmc, expectedNumberOfShifts=100) -->

<!-- MCC.BAMM.df.Constant <- BAMM.extraction.function(MCC.BAMM.ED.Constant) -->

<!-- MCC.BAMM.df.Constant %>% ggplot(aes(x = mean.lambda, y = MCC.BAMM.df$mean.lambda))+ -->
<!--   geom_point() -->
<!-- cor(MCC.BAMM.df.Constant$mean.lambda, MCC.BAMM.df$mean.lambda) -->
<!-- ``` -->

@@

##Subsetted analysis with spectrophotometry data

@@

##Analysis using male-biased measure of sexual selection
